---
title: "CORAM"
author: "Joshua Langfus"
date: "`r Sys.Date()`"
output:
  word_document:
    toc: yes
  pdf_document:
    toc: yes
---

Adapted from supplemental materials from Fried (2017).

```{r setup, include=TRUE, message=FALSE,warning=FALSE}
library(dplyr)
library(tidyr)
library(readxl)
library(purrr)
library('qgraph')
library('ggplot2')
library('data.table')
library('reshape2')
library('psych')
library('ade4')
library('viridis')

set.seed(2023)
knitr::opts_chunk$set(echo = TRUE)
```

# Read Data

```{r dat read}
dat.raw <-
  readxl::read_excel(
    "../data/Expert Symptom Coding.xlsx",
    sheet = "Symptom coding",
    range = "A2:M90",
    col_names = TRUE
  ) %>%
  filter(!is.na(Symptom))%>%
  # select(-2)%>%
  rename(S= `Symptom Label`) %>%
  select(-`Symptom Number`)

dat.binary  <- dat.raw %>%
  filter(is.na(DSMDx)) %>%
  select(-Symptom, -S, -DSMDx) %>%
  mutate(across(everything(), ~if_else(.x == 0,0,1)))
```

```{r fn def}
jaccard <- function(a, b) {
  # dist.binary outputs sqrt(1 - s), where s is similarity coefficient
  # thus, squaring and taking complement returns s (method=1 -> Jaccard coef)
  return(1-(dist.binary(matrix(c(a, b), nrow=2, byrow=TRUE), method = 1)^2))
}
```

# Compute Overlap

```{r overlap}
measures <- colnames(dat.binary)
overlap <- matrix(nrow=length(measures), ncol=length(measures))
rownames(overlap) <- measures
colnames(overlap) <- measures

for( m in 1:length(measures) ) {
  overlap[m, ] <- map_vec(dat.binary, ~jaccard(dat.binary[[m]], .x))
}

overlap[overlap == 1] <- NA # replace diagonal with NA

round(overlap,2)
```

Summary of overlap by measure and overall overlap. Diagonals are ignored (set to NA). This is the final (corrected) version of the analyses presented by Fried.

Since the diagonal is set to `NA`, the function `colMeans()` with `na.rm=TRUE` computes the correct mean overlap for each measure (ignores each measure's overlap with itself).

```{r}
cat('Mean scale overlap\n')
colMeans(overlap, na.rm=TRUE)
cat("Mean overlap: ", mean(colMeans(overlap, na.rm=TRUE)))
```

## Length of scale

```{r}
#NOT DONE YET
```


# Visualization

## Jaccard scores

```{r}
ggcorrplot::ggcorrplot(
  corr = overlap,
  colors = c("red","white","blue"),
  hc.order = TRUE,hc.method = 'ward.D2',
  lab = TRUE,show.legend = FALSE,type = 'lower'
  )
```


## S Overlap Plot

```{r}
dat.plot <- dat.raw  %>%
  filter(is.na(DSMDx)) %>%
  select(-Symptom, -DSMDx) %>%
  pivot_longer(
    cols = -S,
    names_to = "Scale",
    values_to = "Type"
  ) %>%
  rowwise() %>%
  mutate(ScaleNum = grep(Scale,measures)) %>%
  ungroup() %>%
  filter(Type > 0) %>%
  mutate(Type = if_else(Type == 3, 2, Type)) %>%
  mutate(Type = factor(Type, levels=c(1,2), labels=c("Scale contains compound symptom", "Scale contains specific symptom")))

pal1 <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

scale.order <- dat.plot %>%
  group_by(Scale) %>%
    summarise(count_specific = sum(grepl("specific",x=Type)),
            count_compound = sum(grepl("compound",x=Type))
            ) %>%
  arrange(desc(count_specific+count_compound),desc(count_specific),desc(count_compound))
  # summarise(count = n()) %>%
  # arrange(desc(count))

S.order <- dat.plot %>%
  group_by(S) %>%
  summarise(count_specific = sum(grepl("specific",x=Type)),
            count_compound = sum(grepl("compound",x=Type))
            ) %>%
  arrange(desc(count_specific+count_compound),desc(count_specific),desc(count_compound))

dat.plot <- dat.plot %>%
  mutate(S = factor(S, levels = S.order$S),
         Scale = factor(Scale, levels = scale.order$Scale))
  # filter(!(S %in% paste0("S",28:51)))

```

```{r}
p <-
  ggplot(dat.plot,
         aes(
           x = S,
           y = ScaleNum,
           group = S,
           shape = Type,
           color = Scale,
           rev = F
         )) +
  geom_point() +
  coord_polar() +
  xlab("") +
  ylab("") +
  # Generate the grid lines
  geom_hline(
    yintercept = 1:9,
    colour = "grey80",
    linewidth = .2
  ) +
  geom_vline(
    xintercept = 1:54,
    colour = "grey80",
    linewidth = .2
  ) +
  # Points and lines
  geom_line(colour = "grey60") +
  geom_point(size = 3, fill = "white") +
  # Fill the middle space with a white blank rectangle
  geom_rect(
    xmin = -Inf,
    xmax = Inf,
    ymin = -Inf,
    ymax = .6,
    fill = "white",
    color = NA
  ) +
  # Polar coordinates
  scale_shape_manual(values = c(21, 19)) +
  # The angle for the symptoms and remove the default grid lines
  theme(
    # axis.text.x = element_text(angle = 360/(2*pi)*rev( pi/2 + seq( pi/54, 2*pi-pi/54, len=54)) + c(rep(0, 26), rep(180,28))),
    axis.text.y = element_blank(),
    panel.border = element_blank(),
    axis.line = element_blank(),
    axis.ticks = element_blank(),
    panel.grid = element_blank(),
    panel.background = element_blank(),
    legend.position = "right",
    plot.margin = unit(rep(.5, 4), "lines")
  ) +
  labs(fill = "") + # remove legend title
  scale_y_continuous(
    limits = c(-4, 9),
    expand = c(0, 0),
    breaks = 1:length(measures),
    labels = measures
  ) 
  # scale_color_manual(values = pal1)
p
# ggsave("../output/CORAM_Figure1.png",p,width = 60,height=40,units='cm',dpi=300,scale=.35)
```

\newpage

Symptom Key

```{r}
dat.raw %>%
  select(S, Symptom, everything()) %>%
  print(n = 60) #%>%
  # write.csv("../output/Symptom Key.csv")
```




