---
title: "CORAM"
author: "Joshua Langfus"
date: "`r Sys.Date()`"
output:
  word_document:
    toc: yes
  pdf_document:
    toc: yes
---

Adapted from supplemental materials provided in Fried (2017).

TODO: add DSM diagnoses overlay

```{r setup, include=TRUE, message=FALSE,warning=FALSE}
library(dplyr)
library(tidyr)
library(readxl)
library(purrr)
library('qgraph')
library('ggplot2')
library('data.table')
library('reshape2')
library('psych')
library('ade4')
library('viridis')

set.seed(2023)
knitr::opts_chunk$set(echo = TRUE)
```

# Read Data

```{r dat read}
dat.raw <-
  readxl::read_excel(
    "../data/Expert Symptom Coding.xlsx",
    sheet = "Symptom coding",
    range = "A2:M90",
    col_names = TRUE
  ) %>%
  filter(!is.na(Symptom))%>%
  # select(-2)%>%
  rename(S= `Symptom Label`) %>%
  select(-`Symptom Number`)

dat.binary  <- dat.raw %>%
  filter(is.na(DSMDx)) %>%
  select(-Symptom, -S, -DSMDx) %>%
  mutate(across(everything(), ~if_else(.x == 0,0,1)))
```

```{r fn def}
jaccard <- function(a, b) {
  # dist.binary outputs sqrt(1 - s), where s is similarity coefficient
  # thus, squaring and taking complement returns s (method=1 -> Jaccard coef)
  return(1-(dist.binary(matrix(c(a, b), nrow=2, byrow=TRUE), method = 1)^2))
}
```

This function computes the Jaccard index given two vectors of binary data.

# Compute Overlap

```{r overlap}
measures <- colnames(dat.binary)
overlap <- matrix(nrow=length(measures), ncol=length(measures))
rownames(overlap) <- measures
colnames(overlap) <- measures

for( m in 1:length(measures) ) {
  overlap[m, ] <- map_vec(dat.binary, ~jaccard(dat.binary[[m]], .x))
}

overlap[overlap == 1] <- NA # replace diagonal with NA

round(overlap,2)
```

Summary of overlap by measure and overall overlap. Diagonals are ignored (set to NA). This is the final (corrected) version of the analyses presented by Fried.

Since the diagonal is set to `NA`, the function `colMeans()` with `na.rm=TRUE` computes the correct mean overlap for each measure (ignores each measure's overlap with itself).

```{r}
cat('Mean scale overlap\n')
colMeans(overlap, na.rm=TRUE)
cat("Mean overlap: ", mean(colMeans(overlap, na.rm=TRUE)))
```


## Length of scale

```{r}
#NOT DONE YET
```


# Visualization

## Jaccard scores

```{r}
ggcorrplot::ggcorrplot(
  corr = overlap,
  colors = c("red","white","blue"),
  hc.order = TRUE,hc.method = 'ward.D2',
  lab = TRUE,show.legend = FALSE,type = 'lower'
  )
```


## S Overlap Plot

```{r}
dat.plot <- dat.raw  %>%
  filter(is.na(DSMDx)) %>%
  # select(-Symptom, -DSMDx) %>%
  select(-S, -DSMDx) %>%
  rename(S = Symptom) %>%
  pivot_longer(
    cols = -S,
    names_to = "Scale",
    values_to = "Type"
  ) %>%
  rowwise() %>%
  mutate(ScaleNum = grep(Scale,measures)) %>%
  ungroup() %>%
  filter(Type > 0) %>%
  mutate(Type = if_else(Type == 3, 2, Type)) %>%
  mutate(Type = factor(Type, levels=c(1,2), labels=c("Scale contains compound symptom", "Scale contains specific symptom")))

# pal1 <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

scale.order <- dat.plot %>%
  group_by(Scale) %>%
    summarise(count_specific = sum(grepl("specific",x=Type)),
            count_compound = sum(grepl("compound",x=Type))
            ) %>%
  arrange(desc(count_specific+count_compound),desc(count_specific),desc(count_compound))
  # summarise(count = n()) %>%
  # arrange(desc(count))

S.order <- dat.plot %>%
  group_by(S) %>%
  summarise(count_specific = sum(grepl("specific",x=Type)),
            count_compound = sum(grepl("compound",x=Type))
            ) %>%
  arrange(desc(count_specific+count_compound),desc(count_specific),desc(count_compound))

dat.plot <- dat.plot %>%
  mutate(S = factor(S, levels = S.order$S),
         Scale = factor(Scale, levels = scale.order$Scale))
  # filter(!(S %in% paste0("S",28:51)))

```

```{r}
p <-
  ggplot(dat.plot,
         aes(
           x = S,
           y = ScaleNum,
           group = S,
           shape = Type,
           color = Scale,
           rev = FALSE
         )) +
  geom_point() +
  coord_polar() +
  xlab("") +
  ylab("") +
  # Generate the grid lines
  geom_hline(
    yintercept = 1:length(measures),
    colour = "grey80",
    linewidth = .2
  ) +
  geom_vline(
    xintercept = 1:length(unique(dat.plot$S)),
    colour = "grey80",
    linewidth = .2
  ) +
  # Points and lines
  geom_line(colour = "grey60") +
  geom_point(size = 3, fill = "white") +
  # Fill the middle space with a white blank rectangle
  geom_rect(
    xmin = -Inf,
    xmax = Inf,
    ymin = -Inf,
    ymax = .6,
    fill = "white",
    color = NA
  ) +
  # Polar coordinates
  scale_shape_manual(values = c(21, 19)) +
  # The angle for the symptoms and remove the default grid lines
  theme(
    # axis.text.x = element_text(angle = 360/(2*pi)*rev( pi/2 + seq( pi/37, 2*pi-pi/37, len=37)) + c(rep(0, 26), rep(180,28)), hjust = 1),
    axis.text.x = element_text(hjust = 0,vjust=0,angle = 0),
    axis.text.y = element_blank(),
    panel.border = element_blank(),
    axis.line = element_blank(),
    axis.ticks = element_blank(),
    panel.grid = element_blank(),
    panel.background = element_blank(),
    legend.position = "right",
    plot.margin = unit(rep(.5, 4), "lines")
  ) +
  labs(fill = "") + # remove legend title
  scale_y_continuous(
    limits = c(-4, length(measures)),
    expand = c(0, 0),
    breaks = 1:length(measures),
    labels = measures
  ) +
  scale_x_discrete(guide=guide_axis(n.dodge = 5), labels = scales::label_wrap(15))
  # scale_color_manual(values = pal1)
p
# ggsave("../output/CORAM_Figure1.png",p,width = 60,height=40,units='cm',dpi=300,scale=.35)
```

### Tile Version

```{r, fig.width= 10, fig.asp = .7,fig.dpi = 300}
p2 <-
  ggplot(dat.plot, 
         aes(x = Scale, y = S, group = S, fill = Type, rev = FALSE )) +
  geom_tile(width = 1, height = 1) +
  # scale_alpha_discrete(range=c(.5,1))+
  scale_fill_brewer(type = 'qual',palette = 3)+
  scale_x_discrete(guide=guide_axis(n.dodge = 2), labels=scales::label_wrap(10)) +
  theme_classic()
p2
```

## DSM criteria

```{r}
dat.raw  %>%
  filter(!is.na(DSMDx)) %>%
  select(-Symptom) %>%
  # rename(S = Symptom) %>%
  pivot_longer(
    cols = !c(S, DSMDx),
    names_to = "Scale",
    values_to = "Type"
  ) %>%
  rowwise() %>%
  mutate(ScaleNum = grep(Scale,measures)) %>%
  ungroup() %>%
  filter(Type > 0) %>%
  mutate(Type = if_else(Type == 3, 2, Type)) %>%
  mutate(Type = factor(Type, levels=c(1,2), labels=c("Scale contains compound symptom", "Scale contains specific symptom"))) %>%
  
  ggplot(aes(x = Scale, y = S, group = S, fill = Type, rev = FALSE )) +
  facet_wrap(~DSMDx, ncol = 1, scales = 'free',shrink = TRUE,drop = TRUE) +
  geom_tile(width = 1, height = 1) +
  # scale_alpha_discrete(range=c(.5,1))+
  scale_fill_brewer(type = 'qual')+
  scale_x_discrete(guide=guide_axis(n.dodge = 2)) +
  scale_y_discrete(labels = scales::label_wrap(60)) +
  theme_classic()
  
  
```


## Symptom Key

```{r}
dat.raw %>%
  select(S, Symptom, everything()) %>%
  print(n = 60) #%>%
  # write.csv("../output/Symptom Key.csv")
```


# Results

## Properties of the symptoms
Number of symptoms overall
Mean overlap of symptoms across scales
most common / least common symptoms

## Properties of the scales
Number of items on each scale
Idiosyncratic and specific items per scale
Overlap among scales with mean overlap

## Alignment with DSM categories
Items that could plausibly overlap each criterion

# Discussion

Illustrate key findings in terms of amount of overlap overall
Identify scales that are more or less like the others
Comment on whether results across scales would be generalizable
Comment on specific vs. compound items and how there was vast heterogeneity in terms of the specificity of symptoms
Comment on irritability vs. aggression in these scales?

